Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2018-12-22 paper/SI.tex
Implement changes SI with Roman

\section{Supplementary Section 2.       Ion diffusion measurement and calculation}
\label{sec:measure}

@@

>>>>

\section{Ion diffusion measurement and calculation}
\label{sec:measure}

@@

\section{Measurement of charge carrier density of patterned graphene}
\label{sec:charge-dens}
The intrinsic charge carrier density of graphene was measured using a 
field electron transistor (FET) in air with a 300nm SiO$_2$ as a gate.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/charge-dens.png}
  \caption{The I$_{SD}$ as a function of V$_G$. The electron mobility of xyz is extracted from the graph, which very similar to the 
  intrinsic charge carrier density of unpatterned graphene (See Main Text).}
  \label{fig:charge-dens}
\end{figure}
